# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
readActivity <- function() {
  activity <- read.csv("activity.csv", colClasses = c("integer", "Date", "integer"))
  
  within(activity, {
    date = as.factor(date)
  })
}

activity = readActivity()
```


## What is mean total number of steps taken per day?
```{r}
library(plyr)

stepsPerDay <- ddply(activity, .(date), summarize, "steps" = sum(steps))
summary(round(stepsPerDay$steps))
```

```{r,fig.width=11,fig.align='center'}
library(ggplot2, warn.conflicts=F)

qplot(steps, data = na.omit(stepsPerDay), binwidth = 400, alpha = I(0.8),
      main = "Histogram of the total number of steps taken each day")
```

## What is the average daily activity pattern?
Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken,
averaged across all days (y-axis).

```{r,fig.width=11,fig.align='center'}
stepsAverage <- ddply(na.omit(activity), .(interval), summarize, "steps" = round(mean(steps)))
qplot(interval, steps, data = stepsAverage, geom = "line")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
stepsAverage[stepsAverage$steps == max(stepsAverage$steps), "interval"]
```


## Imputing missing values

1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
sum(is.na(activity))
```



## Are there differences in activity patterns between weekdays and weekends?
